---
title: "ds202_lab2"
author: "Tyler Kruzan"
date: "9/17/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Lab 2

```{r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
head(choco)
```

## Individual Questions

###1.How are ratings distributed? Don’t forget to mention outliers, if there are any.
```{r}
hist(choco$Rating, xlab = "Chocolate Rating", main = "Chocolate Ratings Histogram")
boxplot(choco$Rating, xlab = "Chocolate Rating", main = "Chocolate Ratings Boxplot")
```
  
  From what we can see in the histogram above is the there is a relatively strong bell curve or normal distribution of `Chocolate Rating`. he vast majority of ratings were in between 2.5 & 3.5. 
  In the boxplot seen above there are some significant outliers: 4 ratings that landed under the 1st quartile and 1 rating that landed above the 3rd quartile. 


###2.Do ratings depend on the cacao percentage of a chocolate bar?
```{r}
plot(choco$Cocoa.Pct, choco$Rating, xlab = "Chocolate Cocoa %", ylab = "Chocolate Rating")
```
  
  From what can be seen in the scatter plot above, there does not appear to be a relationship between the `Cocoa %` and the `Rating` given to that specific chocolate. Some of the outliers that we can see here are that the highest and lowest rated chcocolate bars are both 70%. There is also a pretty even rating distribution for Cocoa %'s between 55 and 100%.
  
###3.What class is the variable representing company locations? How is this different from a ‘character’ variable? (You do not need to produce a graphic for this question.)
```{r}
class(choco$Company.Location)
```
  From the function I ran above you can see that the class of the `Company.Location` variable is that of a Factor, which is used to represent categorical data and be stored like that of an integer. 

