---
title: "team"
author: "Cameron Stocker & Tyler Kruzan"
date: "9/18/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

``` {r}
choco <- read.csv("https://raw.githubusercontent.com/lbchu/ds202_labs/master/choco.csv")
```

#Question 1

```{r, echo=FALSE}
recent_rating = choco[choco$Review.Date>2011,] #Creates new data frame with more recent reviews from the year 2012 and after

unique(recent_rating$Company.Location) # NOTICE: how many countries are listed but how many levels are there? 
#The unique function cuts out all duplicate values and also the levels that were zero. Explaining why it had less listed than levels.
levels(recent_rating$Company.Location)
recent_rating$Company.Location = droplevels(recent_rating$Company.Location) #Creates a vector that drops the levels with 0 values.

head(recent_rating) #Prints the first 6 values of the updated vector

cross_table = table(recent_rating$Review.Date,recent_rating$Company.Location) #Creates a new table that shows how many reviews were done in each country for each year
cross_table #Prints the table

which(cross_table[1,]!=0 & cross_table[2,]!=0 & cross_table[3,]!=0 & cross_table[4,]!=0 & cross_table[5,]!=0) #Prints the countries that had a review in each year

france_recent = subset(recent_rating,Company.Location =='France') #Creates a new data frame with reviews from only france
uk_recent = subset(recent_rating,Company.Location =='U.K.') #Creates a new data frame with reviews from only the U.K.
germany_recent = subset(recent_rating,Company.Location=='Germany') #Creates a new data frame with reviews from only Germany

par(mfrow=c(2,2)) #Sets up the plots window so that there can by 4 plots on one window in a 2x2 format
color1 = ifelse(france_recent$Rating >median(france_recent$Rating), 'blue', 'green') #Creates a vector of characters where it is "blue" if the rating is higher than the median and "green" if lower than the median
plot(france_recent$Cocoa.Pct ~ france_recent$Review.Date,ylim=c(50,90),col=color1,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "France") #Plots the cocoa percentages for France by year where the ones with "high ratings" are blue and the "low ratings" are green. The yscale is 50 to 90, the point symbol is pch = 18, the size of the symbol is 1.5, the x-axis label is "Review Date", the y-axis label is "Cocoa Percentage", and the plot title is "France".
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('blue','green'),pch=18) #Adds a legend to the plot in the bottom right corner stating that high ratings are blue and low ratings are green

color2 = ifelse(uk_recent$Rating >median(uk_recent$Rating), 'purple', 'red') #Creates a vector of characters where it is "purple" if the rating is higher than the median and "red" if lower than the median
plot(uk_recent$Cocoa.Pct ~ uk_recent$Review.Date,ylim=c(50,90),col=color2,pch=18,cex=1.5, xlab="Review Date", ylab= "Cocoa Percentage", main= "UK") #Plots the cocoa percentages for U.K. by year where the ones with "high ratings" are purple and the "low ratings" are red. The yscale is 50 to 90, the point symbol is pch = 18, the size of the symbol is 1.5, the x-axis label is "Review Date", the y-axis label is "Cocoa Percentage", and the plot title is "UK".
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('purple','red'),pch=18) #Adds a legend to the plot in the bottom right corner stating that high ratings are purple and low ratings are red

color3 = ifelse(germany_recent$Rating > median(germany_recent$Rating), 'orange', 'yellow') #Creates a vector of characters where it is "orange" if the rating is higher than the median and "yellow" if lower than the median
plot(germany_recent$Cocoa.Pct ~ germany_recent$Review.Date,ylim=c(50,90),col=color3,pch=18,cex=1.5,xlab="Review Date", ylab= "Cocoa Percentage", main= "Germany") #Plots the cocoa percentages for Germany by year where the ones with "high ratings" are orange and the "low ratings" are yellow. The yscale is 50 to 90, the point symbol is pch = 18, the size of the symbol is 1.5, the x-axis label is "Review Date", the y-axis label is "Cocoa Percentage", and the plot title is "Germany".
legend('bottomright',legend=c('High Rating', 'Low Rating'),col=c('orange','yellow'),pch=18) #Adds a legend to the plot in the bottom right corner stating that high ratings are orange and low ratings are yellow
```

#Question 2 
Features that could be added to these graphics could include more informative titles, changing the colored data points to shapes would be beneficial for individuals with color blindness. 


#Question 3
```{r}
barplot(table(recent_rating$Review.Date))
barplot(table(choco$Review.Date))
```
Over the years there have been a consistent rise in the number of ratings given out. However, in recent years despite the positive upward trend there has been a fall in the number of ratings given out in in 2016 & 2017

#Question 4
```{r}
sort(table(choco$Company.Location), decreasing = T)
sort(table(choco$Company.Location), decreasing = T)
top3countries = subset(choco, Company.Location == "U.S.A." | Company.Location == "France" | Company.Location == "Canada")
top3countries$Company.Location = droplevels(top3countries$Company.Location)
boxplot(top3countries$Rating ~ top3countries$Company.Location)
```

They all have similar ceilings, France and USA have the two lowest ratings. All of their means are very similar.

#Question 5
Does `Specific.Bean.Origin` have any corellation with `Cocoa.Pct`?

#Quesion 6
```{r}
plot(choco$Specific.Bean.Origin, choco$Cocoa.Pct)
```
Not sure how to answer this question, interesting errors. 

#Submission In Canvas, each team submit an RMarkdown file and (just for insurance) the corresponding html. The file should include the following:

a.  the names of the team members that worked on the document. Tyler Kruzan & Cameron Stocker
b.  a link to the github repo you were working in, the owner’s Github repo name, and his/her username.
(https://github.com/CameronStocker/ds202_lab2.git)
We should be able to see individual1.Rmd, individual2.Rmd, team.Rmd (as well as the corresponding .html files) in the ds202_lab2 repository.
code and answers (including graphics) to all of the questions.
Due date: You have time until Thursday Sept. 19, 10 pm to submit the final files.